The ChEMBL database as Linked Open Data

### 2013-01-14 article.tex
Textual fix: s/once case/one case/
Added a pg on future versions and community support

Once case where Linked Data publishers must avoid implying strong semantics in many cases is
in relation to links to other databases. When linking between two databases based on a shared identifier,
Linked Data publishers make assumptions including syntax assumptions that the identifiers 
are correct and present in the target database, along with semantic assumptions inferring that the
that entries identified in the target database have a scientifically meaningful relationship with the current database.
It is for this reason that the ChEMBL-RDF dataset uses different predicates for linking to various databases.
This problem, however, is general, applying also to other cases where databases link out to third-party sources using identifiers~\cite{VanIersel2010}.

@@

>>>>

One case where Linked Data publishers must avoid implying strong semantics in many cases is
in relation to links to other databases. When linking between two databases based on a shared identifier,
Linked Data publishers make assumptions including syntax assumptions that the identifiers 
are correct and present in the target database, along with semantic assumptions inferring that the
that entries identified in the target database have a scientifically meaningful relationship with the current database.
It is for this reason that the ChEMBL-RDF dataset uses different predicates for linking to various databases.
This problem, however, is general, applying also to other cases where databases link out to third-party sources using identifiers~\cite{VanIersel2010}.

@@

The ongoing ChEMBL-RDF project is Open Source making it possible to others to convert ChEMBL to RDF too.
The ChEMBL team (JO, AG, MD) plans to be a primary source of a RDF version of ChEMBL, while others continue
exposing ChEMBL as RDF too (EW, PA). Various version may arise, exposing the data in different ontologies,
supporting community needs, though convergence may arise after a period of experimenting with ontologies that
will not survive the test of time. The availability of Open Source scripts ensure an easy switch from one
ontology to another.
